Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-05-07 ms.tex
close to a complete introduction of the two-component emission model

% mention that the two different emissivity power laws allow 
% the model to simultaneously explain narrow SED peak, and flattening
% of SED toward the millimeter
At sufficiently high frequencies, Galactic thermal dust emission can be 
adequately modeled as a single MBB with power-law emissivity 
\citep[e.g. SFD;][]{planckdust}. However, it has long been recognized, 
particularly in view of the FIRAS spectra, that the dust SED flattens toward 
the millimeter in a manner which is not consistent with a simple extrapolation 
of the single-MBB model to low frequencies. In the diffuse ISM, \cite{reach95} 
found an improved fit to the FIRAS data using a superposition of two $\beta$=2 
MBBs, one representing a `hot' grain population ($T$$\approx$), the other a 
`cold' grain population ($T$$\approx$).

We adopt the thermal dust emission model of FDS99, which consists of two 
populations of dust grains emitting as MBBs, each with distinct 
emission/absorption characteristics. Importantly, the emissivity power law 
indices $\beta$ of the two species differ. The shape of this spectrum is given 
by:

@@

In accordance with the conventions of FDS99, $\nu_0$ is chosen to be 3000 GHz.
In principle, one could imagine this two MBB model to be specified by seven 
free parameters for every line of sight: $T_1$, $T_2$, $\beta_1$, $\beta_2$, 
$f_1$, and $q_1$/$q_2$ and the normalization of $M_{\nu}$. However, as 
discussed in FDS99, $T_1$=$T_1$($T_2$, $\beta_1$, $\beta_2$, $q_1/q_2$) is 
fully specified by these other parameters under the assumption that the 
temperature of each species is determined by maintaining thermal equilibrium 
with the same interstellar radiation field (ISRF). $T_1$ is always related to 
$T_2$ via a simple power law, although the prefactor and exponent depend on the
 parameters $q_1/q_2$, $\beta_1$ and $\beta_2$. $q_1/q_2$ encodes the
relative emission/absorption cross-sections of the two dust species, while
$f_1$ dictates the relative amounts of each species present.

>>>>

% mention that the two different emissivity power laws allow 
% the model to simultaneously explain narrow SED peak, and flattening
% of SED toward the millimeter
At sufficiently high frequencies, Galactic thermal dust emission can be 
adequately modeled as a single MBB with power-law emissivity 
\citep[e.g. SFD;][]{planckdust}. However, it has long been recognized, 
particularly in view of the FIRAS spectra, that the dust SED flattens toward 
the millimeter in a manner which is not consistent with a simple extrapolation 
of the single-MBB model to low frequencies. In the diffuse ISM, \cite{reach95} 
found an improved fit to the FIRAS data using an empirically motivated 
superposition of two $\beta$=2 MBBs, one representing a `hot' grain population 
($T$$\approx$16$-$21 K), the other a `cold' grain population 
($T$$\approx$4$-$7 K). FDS99 built a more physically motivated two-MBB model, 
in which different grain emission/absorption properties account for the 
differing temperatures of each population, and these temperatures are coupled 
by assuming thermal equilibrium with the same interstellar radiation field 
(ISRF).

The primary FDS99 analysis considered the grain properties, for example the
emissivity power law indices $\beta$, to be constant over the sky, and 
performed a correlation slope analysis to constrain these parameters with
FIRAS and DIRBE observations. A DIRBE 240$\mu$m/100$\mu$m ratio was used
to account for temperature variation at $\sim$1.3$^{\circ}$ resolution. In this
work we seek to apply FDS99-like emission models to the \PLANCK~data set, which
offers a dramatic enhancement in angular resolution relative to the FIRAS 
spectra. The \PLANCK~data allow us to derive a temperature correction at 
near-\IRAS~resolution, re-evaluate the best-fit global dust properties, and
fit addition parameters of the two-component model as a function of position
on the sky.

% could add a last sentence 'ultimately this allows us to make high-resolution
% foreground and extinction predictions' and/or even find a way to mention
% other predictions, such as polarization/R_v

% in the above paragraph, should I mention the Planck collaboration result
% of beta_mm vs. beta_fir being different, with (beta_fir-beta_mm) > 0

% should i also try to justify why it's worth doing this fit even
% if it's possible to just claim different beta's at different frequencies?

The shape of the two-component spectrum we will consider is given by:

@@

Importantly, the emissivity power law indices $\beta$ of the two species 
differ.In accordance with the conventions of FDS99, $\nu_0$ is chosen to be 
3000 GHz. In principle, one could imagine this two MBB model to be specified by
seven free parameters for every line of sight: $T_1$, $T_2$, $\beta_1$, 
$\beta_2$, $f_1$, and $q_1$/$q_2$ and the normalization of $M_{\nu}$. However, 
as discussed in FDS99, $T_1$=$T_1$($T_2$, $\beta_1$, $\beta_2$, $q_1/q_2$) is 
fully specified by these other parameters under the assumption that the 
temperature of each species is determined by maintaining thermal equilibrium 
with the same ISRF. $T_1$ is always related to $T_2$ via a simple power law, 
although the prefactor and exponent depend on the parameters $q_1/q_2$, 
$\beta_1$ and $\beta_2$. $q_1/q_2$ encodes the relative emission/absorption 
cross-sections of the two dust species, while $f_1$ dictates the relative 
amounts of each species present.
